
\documentclass[11pt]{article}
%\usepackage[margin=0.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{ragged2e}
%\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright
\usepackage{fullpage}

\addtolength{\oddsidemargin}{-.2in}
\addtolength{\evensidemargin}{-.2in}
\addtolength{\textwidth}{.4in}

%\setlength{\topmargin}{2in}

\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.5in}

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newcommand{\tab}{\hspacet *{2em}}

\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} \hfill #2\\ \textbf{\emph{#3}}\\  }}
\newcommand{\employerwithguide}[4]{{ \textbf{#1} \hfill(#2)\\ \textbf{\emph{#3}}\\ \emph{#4}  }}
\newcommand{\project}[3]{{ \textbf{#1} (#2)\\ \emph{#3}\\  }}
\newcommand{\projectnoguide}[2]{{ \textbf{#1} (#2)\\  }}
\newcommand{\contact}[2]{
%\vspace*{-8pt}
\begin{center}
{\LARGE \scshape {#1}}\\
%#2 \lineunder
#2
\end{center}
\vspace*{-8pt}
}
\newcommand{\sbt}{\,\begin{picture}(-1,1)(-1,-3)\circle*{2}\end{picture}\ }
\newcommand{\lbt}{\,\begin{picture}(-1,1)(-1,-3)\circle*{3}\end{picture}\ }
\newenvironment{achievements}{
    \begin{list}{$\lbt$}{
        \topsep 0pt
        \itemsep 0pt
        \addtolength{\leftmargin}{-0.1in}
    }
}
{
    \vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses}[4]{
 \textbf{#1} \hfill{#2}\\
    #3\\
\vspace*{5pt}
}
\newcommand{\school}[4]{
 \textbf{#1} #2 $\bullet$ #3\\
#4 \\
}

% END RESUME DEFINITIONS

\begin{document}

\pagenumbering{gobble}

\small
\smallskip
\vspace*{-35pt}

\contact{Lim Chang Siang}
{email: me@changsiang.net $\sbt$ hp: +65-8201 0357 $\sbt$ project: https://www.changsiang.net/projects}

\header{Professional Experience}
\vspace{2mm}
\schoolwithcourses{Research Assistant at Saw Swee Hock School of Public Health (NUS)}{Aug 2018 - Present}
{Primary role as a full-stack developer, developed iOS applicaton and web application to support tele-health 
research projects. Developed requirement documentation for software projects. Developed server-side application in NodeJS and deployment onto UNIX server and cloud platform (AWS)
Conduct user interview to elicit requirements for application development and 
prepare requirement documentations. (Objective-C, NodeJS, Angular 8, .NET, IIS, Linux)}
\hfill{}

\schoolwithcourses{Intern at Singapore Institute of Manufacturing Technology (A*STAR)} {2018 - 2018}
{Primary role as Software Engineer Intern at SIMTech. Developed a PWA application using Ionic Framework and Cordorva for the monitoring of sensor status on the factory floor.
Proposed new UI/UX design for the existing application to solve stakeholder painpoints. Responsible for setting Windows Server for the deployment of the application.
Exceed supervisor expectation by completing the project ahead of schedule. Took on a side-project on proposing solution to monitor energy usage for mobile power generator.
(TypeScript, JavaScript, .NET Framework, IIS, Ionic, Cordorva)}
\hfill{}

\schoolwithcourses{Research Officer at Institute of Molecular and Cell Biology (A*STAR)}{
2015 - 2017}
{My primary task is to conduct experiments on diabetes-related research project. 
Developed stem cell differentiation protocol to derive pancreatic beta cell from 
human induced-pluripotent stem cells. Spearheaded new technique in the lab, including: 
flow cytometry, con-focal microscopy and immunohistochemistry. Perform data analysis on 
Next Generation Sequencing data (ChIPSeq, RNASeq, Metabolomics and SC-Seq). 
Co-authored 3 research publications and 1 review article in the lab.}
\hfill{}

\header{Software Projects}
\vspace*{2mm}

\schoolwithcourses{Remote Home Assessment (iOS Application)}{2018 - 2020}
{This is a research project to evaluate the fesibility of providing remote home assessment service in Singapore.
    
Role: Requirement Collection, Architecture Desgin, Code Implementation, Deployment

Achievements: Used by Occuptation Therapists from 2 restructured hospital in Singapore to evaluate the fesibility of remote OT care.


Tech Stack: Objective-C (iOS), NodeJS, Amazon Web Service ,OSX Server}

\schoolwithcourses{HOPE Personalised Health Kit}{2018 - 2018}
{This application help people with heart disease (CVD) risk to build their self-care plan to reduce their CVD risk.
    
Role: Requirement Research, UI and UX design, Code Implementation, Deployment

Achievements: Project is presented on World Heart Day as part of the CVD prevention program.

Tech Stack: Angular 8, NodeJS (Email Server), Amazon Web Service, Docker Container, Nginx}


\hfill{}

\header{Education}
\vspace{2mm}
\schoolwithcourses{National University of Singapore, Singapore}{2017 - 2018}
{Graduate Diploma in System Analysis. CGPA: 4.58/5.00}

\schoolwithcourses{University of Bradford, United Kingdom}{2015}
{Bachelor of Science (Hons) in Biomedical Science. First Class Honours}
\hfill{}


\header{Research Publications} {*(co-first authors)}
\vspace{2mm}
\begin{achievements}
\justifying
\item {*Ng, N. H. J., *Joanita, B. J., \textbf{Lim, C. S.}, Lau, H. H., Vidhya, G. K., et al., (2019). 
\textbf{HNF4A haploinsufficiency in MODY1 abrogates liver and pancreas differentiation from 
patient-derived iPSCs.} iScience, 16(1). doi: 10.1016/j.isci.2019.05.032}
\item {Teo, A. K., \textbf{Lim, C. S.}, Cheow, L. F., Kin, T., Shapiro, J. A., Kang, N.Y, Lau, H. H. (2018). 
\textbf{Single-cell analyses of human islet cells reveal de-differentiation signatures.} 
Cell Death Discovery, 4(1). doi:10.1038/s41420-017-0014-5}
\end{achievements}
\hfill{}

\header{Other Publications (Reviews or Other Articles)}
\vspace*{2mm}
\begin{achievements}
\justifying
\item Low, B. S., \textbf{Lim, C. S.} (2019). 
\textbf{Scientific and Technological Advancement in Diabetes Management} 
\textit{Biotech-Connection Singapore}
\item {Loo, L. S., Lau, H. H., Jasmen, J. B., \textbf{Lim, C. S.}, and Teo, A. K. (2017). 
\textbf{An arduous journey from human pluripotent stem cells to functional pancreatic beta cells. 
Diabetes, Obesity and Metabolism}, 20(1), 3-13. doi:10.1111/dom.12996}
\end{achievements}
\hfill{}

\header{Conference Presentation}
\vspace*{2mm}
\begin{achievements}
\justifying
\item Charis Anna Lim, Pin Sym Foong, \textbf{Chang Siang Lim}, Gerald Choon-Huat Koh, Shih-Cheng Yen, Author Tay, and Simon Perrault
(2019). \textbf{Supporting Remote Caregiver Input for Home Assessments} at 
\textit{Workgroup on Interactive System in Health @ CHI}
\item Nur Shabrina Amirrudin, Munirah Mohamad Santosa, \textbf{Chang Siang Lim}, 
Hwee Hui Lau, and Adrian Kee Keong Yeo (2016). 
\textbf{Differentiation and characterization of hiPSC-derived pancreatic beta-cells as a model 
to study diabetes.} at \textit{Modelling Cell Fate and Development Conference}
\item \textbf{Chang Siang Lim}, Hwee Hui Lau, Adrian Kee Keong Teo (2015). 
\textbf{Human Cellular Model to Study Diabetes Mechanisms.} at 
\textit{Opportunities and Challenges in Stem Cell Medicine Conference}
\end{achievements}
\hfill{}

\header{Teaching / Mentorship}
\vspace{2mm}
\begin{achievements}
\justifying
\item Wang Liran, Grad Dip in System Analysis, NUS-ISS (2019 - 2020). 
\textit{Develop a novel Augmented-Reality tool to enable Tele-Home Assesmsent by Occupational Therapist.}
\textbf{Role: Technical Advisor}
\item Tan Wei Shan, Grad Dip in System Analysis, NUS-ISS (2019 - 2020).
\textit{Develop a research platform to support the investigation on effective health communication in disease preventions.}
\textbf{Role: Technical Advisor}
\end{achievements}
\hfill{}

\header{Technical Skills}
\vspace{2mm}
\begin{achievements}
\justifying
\item Biostatistic
\item Programming Language: Python, R, Objective-C, C-sharp, Java, JavaScript, SQL
\item Application Development: ASP .NET, iOS, Android, Angular
\item Others: Design Thinking, Objective-Oriented Programming
\end{achievements}
\hfill{}

\header{Other Activities}
\vspace{2mm}
\schoolwithcourses{iShine Befriender at Punngol Family Service Center}{ Aug 2018-Present} 
{As a befrinder, my role is to provide a positive role model to the kids, build confidence and help them to discover their inner talent and strength. In addition, I have also work with the team to develop thematic, hands-on exploratory learning activities for the program}
\hfill{}
   
\header{Other Courses}
\vspace{2mm}
\begin{achievements}
\item Statistical Analysis with R for Public Health Specialization (2019). Provider: Coursera (in collaboration with Imperial Collage London)
\item The Data Scientist's Toolbox (2018). Provider: Coursera (in collaboration with Johns Hopkins University)
\item Introductory Bioinformatics with Scientific Phone Apps Workshop (2017). Provider: Temasek Polytechnic (in collaboration with A*STAR)
\end{achievements}
\hfill{}


\end{document}